Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-10 IUI2021/paper.tex
...

%
%
%

@@

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[IUI '21]{IUI '21: ACM Conference}
  {June 03--05, 2020}{Somewhere, Italy}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

@@

If the user wants to know more about the command line,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{../../GitHelp/paper/figures/info-xxl.png}}
button and see the wiki page\footnote{
  A wiki system {\SB} (\ssf{https:{\slash}{\slash}Scrapbox.io{\slash}product{\slash}}) is used for the data sharing.
} shown in Figure \ref{scrapboxpage}.
The user can edit the page if he wants to add information or finds an error.
In this page, description part is preceded by a ``\texttt{\$}'' symbol and
the command part is preceded by ``\texttt{\%}''.

@@

\begin{figure}[H]
  \centering
  % \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
  \includegraphics[width=7cm,bb=0 0 1982 1536]{figures/a0ba0873eeada33fad1bc383598f90c1.png}
  \includegraphics[width=7cm,bb=0 0 1672 1472]{figures/6b491f2701af7193030e332686733568.png}
  \caption{PayPay Freemarket}
  \label{paypayhf}
  %\Description{PayPay}
\end{figure}

@@

The data used in {\HL} are represented as ``{\SB}'' documents
shown in Figure \ref{scrapboxpage}.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like using text editors.

% \begin{figure}[htb]
% \begin{verbatim}
% \end{verbatim}
% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{../../GitHelp/paper/figures/scrapbox1.png}}
% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{../../GitHelp/paper/figures/scrapbox1.png}}
% \caption{A {\SB} page for \tt{git diff}.}
% \label{xxxxx}
% \end{figure}

@@

Text input systems for non-English languages are widely used
in the world,
and they are called as ``Input Methods'' (IMs).
%
Many research and development on IMs have been going on for years, and
people are using them every day for entering texts in their mother language.
Figure \ref{gyaim} shows an example of a Japanese IM.

\begin{figure}[H]
  % \includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}
  \centerline{\includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}}
  \caption{An IM for Japanese text input.}
  \label{gyaim}
\end{figure}

@@

\subsection*{Other applications of ExpandSearch}

Since the translation mechanism of {\ES} is simple and flexible,
it can be used for a wide range of application domains where
intelligent help is required.
{\ES} is actually used as the help page for
one of our Web services, hoping that
novice users can easily find the feature they need.
When a user submits a query that includes vocabularies
not in the {\ES} document,
we are able to add them to the {\SB} database easily.

Figure \ref{mac1} and Figure \ref{mac2} shows how
{\ES} can be used as a launcher for MacOS.
Like {\HL}, users can execute concrete commands only by
showing small fragments of their intentions to the system.

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
  \centerline{\includegraphics[width=7cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
  \caption{Using {\ES} in the menu bar of MacOS.}
  \label{mac1}
\end{figure}

\begin{figure}[h]
  %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
  \centerline{\includegraphics[width=7cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
  \caption{Using {\ES} in the menu bar of MacOS.}
  \label{mac2}
\end{figure}

>>>>

%
% IUI2021 HelpLine (GitHelp)
%

@@

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[IUI '21]{IUI '21: ACM Conference}
  {April 13--17, 2021}{College Station, AZ}
\acmBooktitle{IUI '21: ACM Symposium on Intelligent User Interface,
  April 13--17, 2021, College Station, AZ}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
  <concept>
    <concept_id>10002951.10003317.10003338.10010403</concept_id>
    <concept_desc>Information systems~Novelty in information retrieval</concept_desc>
    <concept_significance>500</concept_significance>
  </concept>
  <concept>
    <concept_id>10003120.10003121.10003124.10010862</concept_id>
    <concept_desc>Human-centered computing~Command line interfaces</concept_desc>
    <concept_significance>500</concept_significance>
  </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Novelty in information retrieval}
\ccsdesc[500]{Human-centered computing~Command line interfaces}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}

@@

If the user wants to know more about the command line,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{../../GitHelp/paper/figures/info-xxl.png}}
button and see the {\SB}\footnote{
  \ssf{https:{\slash}{\slash}Scrapbox.io{\slash}product{\slash}}
} wiki page shown in Figure \ref{scrapboxpage}.
The user can edit the page if he wants to add information or finds an error.
In this page, description part is preceded by a ``\texttt{\$}'' symbol and
the command part is preceded by ``\texttt{\%}''.

@@

% \includegraphics[width=7cm,bb=0 0 1290 1090]{figures/eaa80e41ddc3d3620fae133007274573.png}
% \includegraphics[width=7cm,bb=-50 0 950 800]{figures/eaa80e41ddc3d3620fae133007274573.png}

\begin{figure}[H]
  \centering
  % \includegraphics[width=10cm,bb=0 0 1716 1312]{figures/3d964512606a5e25646104a738ab104e.png}
  % \includegraphics[width=9cm,bb=0 0 1982 1536]{figures/a0ba0873eeada33fad1bc383598f90c1.png}
  \includegraphics[width=7cm,bb=-200 0 1400 1400]{figures/a0ba0873eeada33fad1bc383598f90c1.png}
  % \includegraphics[width=9cm,bb=0 0 1672 1472]{figures/6b491f2701af7193030e332686733568.png}
  \includegraphics[width=7cm,bb=-200 0 1200 1300]{figures/6b491f2701af7193030e332686733568.png}
  \caption{FAQ services based on Helpfeel.} 
  \label{paypayhf}
  %\Description{PayPay}
\end{figure}

@@

The data used in {\HL} are represented as {\SB} documents
shown in Figure \ref{scrapboxpage}.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like using text editors.

@@

Text input systems for non-English languages are widely used
in the world,
and they are called as ``Input Methods'' (IMs).
%
Many research and development on IMs have been going on for years, and
people are using them every day for entering texts in their mother language.

% Figure \ref{gyaim} shows an example of a Japanese IM.
% 
% \begin{figure}[H]
%   % \includegraphics[width=8cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}
%   \centerline{\includegraphics[width=7cm,bb=0 0 976 670]{../../GitHelp/paper/figures/nyuuryoku-ime.png}}
%   \caption{An IM for Japanese text input.}
%   \label{gyaim}
% \end{figure}

@@

% \subsection*{Other applications of ExpandSearch}
% 
% Since the translation mechanism of {\ES} is simple and flexible,
% it can be used for a wide range of application domains where
% intelligent help is required.
% {\ES} is actually used as the help page for
% one of our Web services, hoping that
% novice users can easily find the feature they need.
% When a user submits a query that includes vocabularies
% not in the {\ES} document,
% we are able to add them to the {\SB} database easily.
% 
% Figure \ref{mac1} and Figure \ref{mac2} shows how
% {\ES} can be used as a launcher for MacOS.
% Like {\HL}, users can execute concrete commands only by
% showing small fragments of their intentions to the system.
% 
% \begin{figure}[h]
%   %\centerline{\includegraphics[width=8cm,bb=0 0 397 247]{../../GitHelp/paper/figures/clock.png}}
%   \centerline{\includegraphics[width=7cm,bb=0 0 300 200]{../../GitHelp/paper/figures/mac1.png}}
%   \caption{Using {\ES} in the menu bar of MacOS.}
%   \label{mac1}
% \end{figure}
% 
% \begin{figure}[h]
%   %\centerline{\includegraphics[width=8cm,bb=0 0 392 185]{../../GitHelp/paper/figures/mac2.png}}
%   \centerline{\includegraphics[width=7cm,bb=0 0 300 130]{../../GitHelp/paper/figures/mac2.png}}
%   \caption{Using {\ES} in the menu bar of MacOS.}
%   \label{mac2}
% \end{figure}
